### 2017-04-07 paper/evaluation.tex
almost done with RQ5

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      question~\ref{questionThree}.}
\end{wrapfigure}
Considering question 3, \emailsA{} of developers who answered the
survery did not know that parallelism was available in Maven,
\emailsB{} of developers mentioned that they did not use parallelism
because of concerns with concurrency issues, \emailsD{} of developers
uses a continuous integretion server for run tests while working
\Luis{here I want to say that they use it for something like
  "non-blocking testing" while developing in a local machine},
\emailsD{} of developers thinks that it is not worthy the effort, and
\emailsNA{} of developers did not answered the last question, or did
not knew an answer.

\begin{center}
\fbox{
	\begin{minipage}{8cm}
		\textit{Answering \numRQE{}:~\emph{\Luis{summarize
		findings...}}}
	\end{minipage}
}
\end{center}

>>>>

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.15\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.

\begin{center}
\fbox{
	\begin{minipage}{8cm}
	  \textit{Answering \numRQE{}:}~\emph{Results suggest that dealing
       with concurrency issues (\ie{}, the extra work to organize test
       suite to safely explore concurrency) was the principal reason
       for developers not investing in parallelism.  Other reasons
       included availability of continuous integration services and
       unfamiliarity with the technology.}
	\end{minipage}
}
\end{center}
